SLE martingales in coset conformal field theory

### 2012-05-12 AffineLieAlgebras/SLE/paper.tex
Added equation with the drift.
Preliminary version is completed,  comments removed. Ready to be sent to friends.

\newtheorem{statement}{Statement}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}{Lemma}
\newtheorem{mynote}{Note}[section]
%\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}
\newtheorem{example}{Example}
\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
\newcommand{\co}[1]{\stackrel{\circ }{#1}}
\newcommand{\pia}{\pi_{\mathfrak{a}}}
\newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
\newcommand{\gf}{\mathfrak{g}}
\newcommand{\af}{\mathfrak{a}}
\newcommand{\aft}{\widetilde{\mathfrak{a}}}
\newcommand{\afb}{\mathfrak{a}_{\bot}}
\newcommand{\hf}{\mathfrak{h}}
\newcommand{\hfb}{\mathfrak{h}_{\bot}}
\newcommand{\pf}{\mathfrak{p}}
\newcommand{\gfh}{\hat{\mathfrak{g}}}
\newcommand{\afh}{\hat{\mathfrak{a}}}
\newcommand{\bff}{\mathfrak{b}}
\newcommand{\hfg}{\hf_{\gf}}

@@

%%% dates of submition & resubmition (if submitted once, second argument is *)
\dates{26 April 2012}{*}

@@

%% We
%% consider Schramm-Loewner evolution $SLE_{\kappa}$ with additional Brownian motion on coset space
%% $G/A$ characterised by parameter $\tau$ proposed in our paper \cite{2011arXiv1112.4354N}. We consider correlation functions in coset models of
%% conformal field theory which satisfy martingale conditions with respect to this stochastic process.
%% Since all minimal unitary models of conformal field theory can be obtained from coset construction
%% for certain choice of Lie group $G$ and subgroup $A$ \cite{difrancesco1997cft} these correlation functions correspond to SLE
%% observables appearing as the scaling limit of lattice observables. Trace of
%% Schramm-Loewner $\gamma_{t}$ evolution describes critical domain wall in lattice models.
%% 
 Consider some critical lattice model on the upper half-plane $\mathbb{H}$ with the cut along a critical interface $\gamma_{t}$ (domain wall up to some length $t$). We denote this slit domain by $\mathbb{H}_{t}=\mathbb{H}\setminus \gamma_{t}$.  Assume that $\gamma_{t}$ satisfies restriction property and is conformally  invariant \cite{Cardy:2005kh}. Then  conformal map  $g_{t}:\mathbb{H}_{t}\to \mathbb{H}$ satisfies stochastic differential equation \cite{schramm2000scaling}:
\begin{equation}
\label{eq:19}
  \frac{\partial g_t(z)}{\partial t} = \frac{ 2}{g_t(z)-\sqrt{\kappa}\xi_{t}} ,
\end{equation}
where $\xi_{t}$ is the Brownian motion. The dynamic of the tip $z_{t}$ of critical curve $\gamma_{t}$ (tip of SLE trace) is given by the law $z_{t}=g_{t}^{-1}(\sqrt{\kappa}\xi_{t})$.

@@

\subsection{Examples}
\label{sec:examples-1}
As an example consider  $\frac{\hat{su}(2)_{N}}{\hat{u}(1)_{N}}$-coset models which are equivalent to $Z_{N}$-parafermions.  The central charge is $c=\frac{3N}{N+2}-1=\frac{2N-2}{N+2}$. Conformal weights of primary fields with Dynkin indeces $(k,l)$ are $h_{(k,l)}=\frac{k(k+2)}{4(N+2)}-\frac{l^{2}}{4N}$.
% $C_{\mu}=k(k+2)/2, C_{\nu}=l^{2}/2$

@@

%% But correlation functions in coset conformal field theory must satisfy (generalized) Knizhnik-Zamolodchikov equations \cite{kogan1997knizhnik} which are of the form
%% \begin{equation}
%%   \label{eq:16}
%%  \left[ \frac{1}{2}\frac{\partial}{\partial w_{i}} +\sum_{j\neq i} \left( \frac{\sum_{a}t_{i}^{a}t_{j}^{a}}{k+h^{\vee}}-\frac{\sum_{b}\tilde t_{i}^{b}\tilde t_{j}^{b}}{x_{e}k+h_{\af}^{\vee}}\right) \right]\mathcal{F}_{\mathbb{H}}=0
%% \end{equation}
%% Rewrite the equation as
%% \begin{equation}
%%   \label{eq:22}
%%   \left[ \frac{1}{2}\frac{\partial}{\partial w_{i}} +\sum_{j\neq i} \left( \frac{\sum_{a}t_{i}^{a}t_{j}^{a}}{k+h^{\vee}}-\frac{\sum_{b}\tilde t_{i}^{b}\tilde t_{j}^{b}}{x_{e}k+h_{\af}^{\vee}}\right) \right]\mathcal{F}_{\mathbb{H}}=0
%% \end{equation}
%% 
%% From this relations and equation \eqref{eq:8} we can write sufficient conditions for SLE martingale to be CFT correlation function:
%% \begin{equation}
%%   \label{eq:23}
%%   M x = 0
%% \end{equation}
%% 
%% It is also possible to consider coset theory as $G\times A$  gauge theory and impose constraints on physical states later (See \cite{hwang1993brst,kogan1997knizhnik,gawdzki1988g,figueroa89equivalence}). In this case second term in equation \eqref{eq:3} will include sum over $\gf$ and $\af$ generators and two parameters of Brownian motion $\tau_{\gf}$ and $\tau_{\af}$. 
%% 
\section{Conclusion and outlook}
\label{sec:outlook}

@@

Massive perturbations of $G/A$-coset theory are realized as an affine Toda field theory and are classified by simple roots of the Lie algebra $\gf$.

It is possible to get the perturbed theory from the action \cite{bakas1996lagrangian,hollowood1995massive,park1994deformed}
\begin{equation}
  S_{\text{pert}}=S_{G/A}(\gamma,\alpha)-\frac{k\lambda}{2\pi}\int {\cal K} (\gamma T, \gamma^{-1} \bar T),
\end{equation}
where $T,\bar T\in \gf$ are specially chosen Lie algebra elements.

For example consider  $\frac{\hat{su}(2)_{N}\oplus \hat{su}(2)_{1}}{\hat{su}(2)_{N+1}}$-coset realization of minimal unitary models. Then we get perturbation by $\phi_{(2,1)}$ primary field from the action
\begin{equation}
  S=S_{\frac{\hat{su}(2)_{N}\oplus \hat{su}(2)_{1}}{\hat{su}(2)_{N+1}}} (\gamma_1,\gamma_2,\alpha,\bar \alpha) - \frac{k\lambda}{2\pi}\int Tr(\gamma_1^{-1} \gamma_2+\gamma_2^{-1}\gamma_1)
\end{equation}

Massive off-critical SLEs have additional drift term in driving Brownian motion \cite{makarov2010off}. Inclusion of a drift term in (\ref{eq:20}) leads to the  appearance of new terms in the martingale condition (\ref{eq:8}).

On the other hand the perturbation can be seen as an insertion of certain primary field in all the correlation functions \cite{hollowood1989rational}. The question is whether the interaction of this primary field with the $\tau$-term of the equation (\ref{eq:4}) leads to the same contribution as the addition of a massive drift to SLE.

Domain walls in the Ising model perturbed by a random Gaussian external field were studied numerically using Schramm-Loewner evolution in a recent paper \cite{stevenson2011domain}. In the forthcoming studies we will compare this results with massive perturbations.

@@

%%  
%%  
%%  
%%  Coset  models are specified by Lie algebra
%%  $\gf$ and its subalgebra $\af$. Denote by $J_{n}^{a}$ the generators of affine Lie algebra $\gfh$
%%  and by $\tilde{J}_{n}^{b}$ the generators of $\afh$, so that $\tilde{J}^{b}_{n}=\sum_{a} m_{a}^{b}
%%  J^{a}_{n}$. 
%%  Virasoro generators in coset models are given by the difference of Sugawara expressions
%%  of $\gf$ and $\af$-WZNW models:
%%  \begin{equation*} L_{n}=L_{n}^{\gf}-L_{n}^{\af}
%%  \end{equation*}
%%   Commutation relations of Virasoro generators with generators of subalgebra $\afh$
%%  are trivial
%%  \begin{equation}
%%    \label{eq:26} \left[L_{n},\tilde{J}^{b}_{m}\right]=0
%%  \end{equation}
%%  
%%  Commutation relations between generators of $\gfh$ and Virasoro generators are now
%%  \begin{equation}
%%    \label{eq:1}
%%    \left[ L_{n}, J_{m}^{a} \right] = [L_{n}^{\gf}-L_{n}^{\af},J_{m}^{a}]= 
%%  \end{equation}
%%  
%%  Coset models can be realized as gauged Wess-Zumino-Novikov-Witten models by adding gauge fields
%%   $A,
%%  \bar{A}$ taking values in Lie algebra $\af\subset \gf$ to the action\cite{gawdzki1988g}.
%%   Then fields
%%  are labeled by pairs of weights $(\mu,\nu)$, where $\mu$ is the weight of $\gfh$ and $\nu$ is the
%%  weight of $\afh$ correspondingly. But there are selection rules, i.e. the branching functions for
%%  certain pairs of weights $(\mu,\nu)$ vanish. There is also a redundancy, i.e. non-vanishing
%%  branching functions for distinct pairs $(\mu,\nu)$ turn out to be identical
%%  \cite{fuchs1996resolution,schellekens1990field}.
%%  
%%  So, primary fields are labeled by pairs of weights $(\mu,\nu)\in \hf_{\gfh}\oplus \hf_{\afh}$ of
%%  algebra $\gfh$ and subalgebra $\afh$, such that branching functions $b^{\mu}_{\nu}(q)\neq 0$. Some
%%  pairs are equivalent. This equivalence is given by the action of so called ``simple currents''
%%  $(J,\tilde{J})$, which are certain elements of outer automorphisms group $\mathcal{O}(\gfh)\times
%%  \mathcal{O}(\afh)\approx B(G)\times B(A)$ of $\gfh\times\afh$, where $B(G)$ is center of Lie group
%%  G. We can think of simple currents as of primary fields and their action on fields of theory are
%%  then given by fusion product \cite{difrancesco1997cft}. So primary fields of coset model are given
%%  by the equivalence classes of pairs of weights $(\mu,\nu)\sim (J*\mu,\tilde{J}*\nu)$, where
%%  $(J,\tilde J)$ such that their conformal weights are equal: $h_{J}-h_{\tilde{J}}=0$.
%%  
%%  Conformal weight of coset primary field is equal to
%%  \begin{multline}
%%  L_0\left|\phi_{(\mu,\nu)}\right>=\left(\frac{1}{2(k+h^{\vee})}\sum_aJ^a_0J^a_0-\frac{1}{2(k+h_{\af}^{\vee})}\sum_b
%%  \tilde{J}^b_0 \tilde{J}^b_0 \right) \left|\phi_{(\mu,\nu)}\right>=\\
%%  \left(\frac{(\mu,\mu+2\rho)}{2(k+h^{\vee})}-\frac{(\nu,\nu+2\rho_{\af})}{2(k+h^{\vee})}\right)\left|\phi_{(\mu,\nu)}\right>
%%  \end{multline} It is possible to obtain analogues of Knizhnik-Zamolodchikov equations for coset
%%  models \cite{kogan1997knizhnik}:
%%  \begin{equation} \left\{\frac{1}{2}\partial_{i} + \sum_{i\neq
%%  j}^{N}\left(\frac{t^{a}_{i}t^{a}_{j}}{k+h^{\vee}}-\frac{\tilde t^{b}_{i}\tilde
%%  t^{b}_{j}}{k+h^{\vee}_{\af}}\right)\frac{1}{z_{i}-z_{j}}\right\} \left<\phi_{1}(z_{1})\dots
%%  \phi_{N}(z_{N})\right>=0
%%    \label{eq:6}
%%  \end{equation}
%%  
%%  Let us introduce Schramm-Loewner evolution corresponding to coset models. The idea is to constrain
%%  additional Brownian motion on group manifold to the factor space $G/A$.
%%  
%%  
%%  To study SLE on $G/A$ factor space we restrict random walk on group manifold by the choice of basis
%%  in $\gf$. Assume that generators $\{J^{a};\; a=1\dots \dim\gf\}$ are chosen in such way that
%%  $\mathcal{K}(J^{a},J^{b})=h^{\vee}\delta_{ab}$ and $\{J^{a};\;
%%  a=\dim\gf-\dim\af\dots \dim\gf\}$ are the generators of subalgebra
%%  $\af\subset \gf$. Now we can consider $(\dim\gf-\dim\af)$-dimensional Brownian
%%  motion with generators $d\theta^{a}$ such that $\mathbb{E}(d\theta^{a} \;
%%  d\theta^{b})=\delta_{ab};\; a,b=1,\dots,\dim\gf-\dim\af$.
%%  
%%  Then for generator of field transformation we can write
%%  \begin{equation} \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa}
%%  d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a=1}^{\dim\gf-\dim\af}\left(d
%%  \theta ^{a} t^{a}_{i}\right)\right)
%%  \label{eq:5}
%%  \end{equation}
%%   Substituting to equation \eqref{eq:8} we get martingale condition
%%  
%%  \begin{equation} \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa
%%  \mathcal{L}_{-1}^{2}+\frac{\tau}{2}\left( \sum_{a=1}^{\dim\gf-\dim\af}
%%  \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}\right)\right) \mathcal{F}_{\mathbb{H}}=0
%%  \label{eq:9}
%%  \end{equation}
%%  
%%  which can be rewritten as the requirement for
%%  \begin{equation} \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau
%%  \left(\sum_{a=1}^{\dim\gf-\dim\af}J^{a}_{-1}J^{a}_{-1}\right)\right)
%%  \phi_{(\mu,\nu)}
%%  \label{eq:10}
%%  \end{equation}
%%   to be level two null-field.
%%  
%%   It is not always convenient to work with generators
%%  orthogonal with respect to Killing form $\mathcal{K}$, sometimes it is preferable to use Chevalley
%%  or Cartan-Weyl basis. So we change normalization condition of additional
%%  $\dim\gf$-dimensional Brownian motion \eqref{eq:5} to $\mathbb{E}\left[d\theta^{a}\;
%%  d\theta^{b}\right]=\mathcal{K}(t^{a},t^{b})dt$, and the generator of field transformation
%%  \eqref{eq:2} is
%%  \begin{equation*} \mathcal{G}_{i}=\left(\frac{2dt}{w_{i}}-\sqrt{\kappa}
%%  d\xi_{t}\right) \partial_{w_{i}}+\frac{\sqrt{\tau}}{w_{i}}\left(\sum_{a:\mathcal{K}(t^{a},\tilde{t}^{b})=0}\left(d
%%  \theta ^{a} t^{a}_{i}\right)\right).
%%  \end{equation*}
%%   Martingale condition \eqref{eq:8} can be written as
%%  \begin{equation*} \left(-2 \mathcal{L}_{-2}+\frac{1}{2}\kappa
%%  \mathcal{L}_{-1}^{2}+\frac{\tau}{2}\left( \sum_{a} \mathcal{J}^{a}_{-1} \mathcal{J}^{a}_{-1}-
%%  \sum_{b}\tilde{\mathcal{J}}^{b}_{-1} \tilde{\mathcal{J}}^{b}_{-1}\right)\right)
%%  \mathcal{F}_{\mathbb{H}}=0.
%%  \end{equation*}
%%   This equation can again be rewritten as the requirement for
%%  \begin{equation} \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau
%%  \left(\sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\dim\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right)
%%  \phi_{(\mu,\nu)}
%%  \label{eq:30}
%%  \end{equation}
%%   to be level two null-field.
%%  
%%  Acting with $L_{2}$ we get
%%  \begin{equation*}
%%    L_{2}\psi= \left(-8 L_{0}+c/2+ 3 \kappa L_{0}+\frac{1}{2}\tau k \dim\gf\right)
%%  \phi_{(\mu,\nu)}
%%  \end{equation*}
%%  \begin{equation}
%%    \label{eq:28} (3\kappa-8) h_{(\mu,\nu)}+c+\tau k =0
%%  \end{equation}
%%  
%%  Now we act with $L_{1}^{2}$  and obtain
%%  \begin{equation}
%%    \label{eq:17} 12 h_{(\mu,\nu)}+2\kappa h_{(\mu,\nu)} (2h_{(\mu,\nu)}+1) + \tau
%%  (C_{\mu}-\tilde{C}_{\nu})=0,
%%  \end{equation}
%%   where $C_{\mu}=(\mu,\mu+2\rho)$ is the eigenvalue of quadratic Casimir operator
%%  $\sum_{a}t^{a}t^{a}$. We need to get one more equation since we
%%  have three variables $\kappa,\tau,h_{(\mu,\nu)}$. We can use that $\psi$ is singular vector so
%%  $L_{1}\psi=0$ and then $J_{1}^{a}L_{1}\psi=0,\; \tilde{J}_{1}^{b} L_{1}\psi=0$, so
%%  
%%  \begin{equation}
%%  L_{1} \psi=L_{1}\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau
%%  \left(\sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{-1}-\sum_{b=1}^{\dim\af}\tilde{J}^{b}_{-1}\tilde{J}^{b}_{-1}\right)\right)
%%  \phi_{(\mu,\nu)}
%%  \end{equation}
%%  
%%  \begin{equation*}
%%  L_{1}\psi = \left(-6 L_{-1}+\kappa (2  L_{-1} L_{0}+L_{0}) + \tau \sum_{a=1}^{\dim\gf}J^{a}_{-1}J^{a}_{0}\right)
%%  \phi_{(\mu,\nu)}
%%  \end{equation*}
%%  \begin{equation*}
%%    L_{1}^{2}\psi= \left(-12 L_{0}+\kappa (4  L_{0}^{2}+2 L_{0}) + \tau \sum_{a=1}^{\dim\gf}J^{a}_{0}J^{a}_{0}\right)
%%  \phi_{(\mu,\nu)}
%%  \end{equation*}
%%  \begin{equation*}
%%    J_{1}^{a}L_{1} \psi= \left(-6 J_{0}^{a}+\kappa (2  J_{0}^{a} L_{0}+J_{0}^{a}) + \tau
%%      \sum_{b=1}^{\dim\gf}\sum_{c=1}^{\dim\gf}i f^{abc}J^{c}_{0}J^{b}_{0}+k\tau J_{0}^{a}\right)
%%  \phi_{(\mu,\nu)}
%%  \end{equation*}
%%  
%%  
%%  \begin{equation*}
%%    L_{2}\psi= \left(-8 L_{0}+c/2+ 3 \kappa L_{0}+\frac{1}{2}\tau k \dim\gf\right)
%%  \phi_{(\mu,\nu)}
%%  \end{equation*}
%%  
%%  \begin{eqnarray*}
%%    (3\kappa-8) h_{(\mu,\nu)}+c/2+\frac{1}{2}\tau k \dim\gf=0\\
%%    -12 h_{(\mu,\nu)}+\kappa (4 h_{(\mu,\nu)}^{2}+2 h_{(\mu,\nu)}) +\tau C(\mu) =0\\
%%    (-6 +\kappa (2 h_{(\mu,\nu)}+1)+\tau
%%  \end{eqnarray*}
%%  \begin{equation}
%%    \label{eq:29} \left(-6 + \kappa + \tau + 2 \kappa h_{(\mu,\nu)}\right) J^{3}_{0}
%%  \phi_{(\mu,\nu)}=0
%%  \end{equation}
%%  
%%  Acting on \eqref{eq:30} with $L_{2}$ and $L_{1}^{2}$ we can obtain equations \eqref{eq:28} and
%%  \eqref{eq:17}. To get more equations we can act by $\afh$-generators $\tilde{J}^{b}_{1}$ and $L_{1}$
%%  similarly to what was done with $J^{3}_{1}$ to get equation \eqref{eq:29}.
%%  
%%  To obtain simpler relations it is also possible to use generalization of Knizhnik-Zamolodchikov
%%  equations \eqref{eq:6} as was done for WZNW-models in paper \cite{alekseev2010sle}.
%%  
%%  
%%  Now consider simple example. Let $G=SU(2)$ and $A=U(1)$, and corresponding Lie algebras
%%  $\gf=\mathrm{su}(2)$ with generators $J^{1},J^{2},J^{3}$ and $\af=\mathrm{u}(1)$ with the generator
%%  $J^{3}$, $\af\subset\gf$. Note that $\mathcal{K}(J^{a},J^{b})=2\delta^{ab}$.
%%  
%%   The equation \eqref{eq:10} is now
%%  \begin{equation}
%%    \label{eq:11} \psi=\left(-2L_{-2}+\frac{1}{2}\kappa L_{-1}^{2}+\frac{1}{2}\tau
%%  \left(J^{1}_{-1}J^{1}_{-1}+J^{2}_{-1}J^{2}_{-1}\right)\right) \phi_{(\mu,\nu)}
%%  \end{equation}
%%   If we use basis $J^{+}=\frac{J^{1}+iJ^{2}}{\sqrt{2}},\;
%%  J^{-}=\frac{J^{1}-iJ^{2}}{\sqrt{2}}$ this equation is rewritten in the form
%%  \begin{equation} \psi= \left(-2
%%  L_{-2}+\frac{\kappa}{2}L_{-1}^{2}+\frac{\tau}{2}\left[J^{+}_{-1}J^{-}_{-1}+J^{-}_{-1}J^{+}_{-1}\right]\right)
%%  \phi_{(\mu,\nu)}
%%  \label{eq:12}
%%  \end{equation}
%%   which is similar to the equations for parafermionic fields introduced in paper
%%  \cite{santachiara2008sle}.
%%  
%%  Central charge in this case is equal to
%%  \begin{equation}
%%    \label{eq:14} c=\frac{2(k-1)}{k+2}
%%  \end{equation}
%%  
%%  Let us study the solutions of the equation \eqref{eq:11}. Act on $\psi$ with $L_{2}$:
%%  \begin{equation}
%%    \label{eq:13} L_{2}\psi=(-8L_{0}+c+3\kappa L_{0}+\tau k)\phi_{(\mu,\nu)}=0,
%%  \end{equation}
%%   and obtain
%%  \begin{equation}
%%    \label{eq:28} (3\kappa-8) h_{(\mu,\nu)}+c+\tau k =0
%%  \end{equation}
%%   Another equation can be obtained by action of $L_{1}^{2}$
%%  \begin{equation}
%%    \label{eq:15} L_{1}^{2}\psi = (12 L_{0} + \kappa(4 L_{0}^{2}+2 L_{0}) +\tau
%%  (J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}))\phi_{(\mu,\nu)}=0
%%  \end{equation}
%%   Since
%%  $J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}=J_{0}^{1}J_{0}^{1}+J_{0}^{2}J_{0}^{2}+J_{0}^{3}J_{0}^{3}-J_{0}^{3}J_{0}^{3}$
%%  we have
%%  \begin{equation}
%%    \label{eq:17} 12 h_{(\mu,\nu)}+2\kappa h_{(\mu,\nu)} (2h_{(\mu,\nu)}+1) + \tau
%%  (C_{\mu}-\tilde{C}_{\nu})=0,
%%  \end{equation}
%%   where $C_{\mu}=(\mu,\mu+2\rho)$ is the eigenvalue of quadratic Casimir operator
%%  $\sum_{a}t^{a}t^{a}$. For $u(1)$ it is just $\nu^{2}$. We need to get one more equation since we
%%  have three variables $\kappa,\tau,h_{(\mu,\nu)}$. We can use that $\psi$ is singular vector so
%%  $L_{1}\psi=0$ and then $J_{1}^{3}L_{1}\psi=0$, so
%%  \begin{equation}
%%    \label{eq:29} \left(-6 + \kappa + \tau + 2 \kappa h_{(\mu,\nu)}\right) J^{3}_{0}
%%  \phi_{(\mu,\nu)}=0
%%  \end{equation}
%%  
%%  
%%  Turn to the case $k=2, \;c=1/2$ which corresponds to square lattice Ising model. We have three
%%  non-equivalent fields numbered by the pairs of $su(2)$ and $u(1)$ weights, which are $\phi_{(0,0)},
%%  \; h_{(0,0)}=0; \quad \phi_{(0,2)}, \; h_{(0,2)}=1/2; \quad \phi_{(1,1)}, \; h_{(1,1)}=1/16$. The
%%  equation \eqref{eq:29} is trivial for $\phi_{(0,0)}$ and $\phi_{(0,2)}$, so the equations
%%  \eqref{eq:17}, \eqref{eq:28} are consistent although we do not know how to interpret $\tau$ in
%%  context of the Ising model. If we consider the field $\phi_{(1,1)}$ we have no solution for
%%  $\kappa,\tau$, so we see that not every primary field corresponds to some boundary condition
%%  changing operator.
%%  
%%  
%%  \section{Algebraic equations}
%%  \label{sec:algebraic-equations}
%%  
%%  \section{Examples}
%%  \label{sec:examples}
%%

>>>>

\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
\newcommand{\co}[1]{\stackrel{\circ }{#1}}
\newcommand{\pia}{\pi_{\mathfrak{a}}}
\newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
\newcommand{\gf}{\mathfrak{g}}
\newcommand{\af}{\mathfrak{a}}
\newcommand{\aft}{\widetilde{\mathfrak{a}}}
\newcommand{\afb}{\mathfrak{a}_{\bot}}
\newcommand{\hf}{\mathfrak{h}}
\newcommand{\hfb}{\mathfrak{h}_{\bot}}
\newcommand{\pf}{\mathfrak{p}}
\newcommand{\gfh}{\hat{\mathfrak{g}}}
\newcommand{\afh}{\hat{\mathfrak{a}}}
\newcommand{\bff}{\mathfrak{b}}
\newcommand{\hfg}{\hf_{\gf}}

@@

%%% dates of submition & resubmition (if submitted once, second argument is *)
\dates{12 May 2012}{*}

@@

 Consider some critical lattice model on the upper half-plane $\mathbb{H}$ with the cut along a critical interface $\gamma_{t}$ (domain wall up to some length $t$). We denote this slit domain by $\mathbb{H}_{t}=\mathbb{H}\setminus \gamma_{t}$.  Assume that $\gamma_{t}$ satisfies restriction property and is conformally  invariant \cite{Cardy:2005kh}. Then  conformal map  $g_{t}:\mathbb{H}_{t}\to \mathbb{H}$ satisfies stochastic differential equation \cite{schramm2000scaling}:
\begin{equation}
\label{eq:19}
  \frac{\partial g_t(z)}{\partial t} = \frac{ 2}{g_t(z)-\sqrt{\kappa}\xi_{t}} ,
\end{equation}
where $\xi_{t}$ is the Brownian motion. The dynamic of the tip $z_{t}$ of critical curve $\gamma_{t}$ (tip of SLE trace) is given by the law $z_{t}=g_{t}^{-1}(\sqrt{\kappa}\xi_{t})$.

@@

\subsection{Examples}
\label{sec:examples-1}
As an example consider  $\frac{\hat{su}(2)_{N}}{\hat{u}(1)_{N}}$-coset models which are equivalent to $Z_{N}$-parafermions.  The central charge is $c=\frac{3N}{N+2}-1=\frac{2N-2}{N+2}$. Conformal weights of primary fields with Dynkin indeces $(k,l)$ are $h_{(k,l)}=\frac{k(k+2)}{4(N+2)}-\frac{l^{2}}{4N}$.

@@

\section{Conclusion and outlook}
\label{sec:outlook}

@@

Massive perturbations of $G/A$-coset theory are realized as an affine Toda field theory and are classified by simple roots of the Lie algebra $\gf$. Affine Toda field theory can be obtained by adding perturbation term to  the action (\ref{eq:24}):
\begin{equation}
  S_{\text{pert}}=S_{G/A}(\gamma,\alpha)-\frac{k\lambda}{2\pi}\int {\cal K} (\gamma T, \gamma^{-1} \bar T),
\end{equation}
where $T,\bar T\in \gf$ are specially chosen Lie algebra elements \cite{bakas1996lagrangian,hollowood1995massive,park1994deformed}. 
The perturbation leads to an insertion of certain primary field in all the correlation functions  \cite{hollowood1989rational}. It was shown that massive off-critical SLEs have additional drift term in driving Brownian motion \cite{makarov2010off,bauer2009off}.
The question is whether the interaction of the perturbing primary field with the $\tau$-term of the equation (\ref{eq:4}) leads to the same contribution as the addition of a massive drift to SLE.

In the forthcoming studies we will address this question and compare  massive perturbations of coset models with the numerical studies of domain walls in the Ising model perturbed by a random Gaussian external field \cite{stevenson2011domain}.

@@
